Sound and Automated Synthesis of Digital Controllers for Continuous Plants

### 2017-03-13 slides/presentation.tex
pres

\begin{frame}{Jury's Criterion}
\begin{equation*}
S(z) = \hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z) = \sum_{i=0}^{N_S} c_iz^{N_s-i}, c_0\neq0. 
\end{equation*}

$$
M=\left( 
\begin{array}{ccc}
v^{(0)}_{1} &\cdots & v^{(0)}_{N_S}\\
v^{(1)}_{1} &\cdots&  v^{(1)}_{N_S}\\
\vdots&\vdots&\vdots\\
v^{(N_S-1)}_{1} &\cdots&  v^{(N_S-1)}_{N_S}\\
\end{array}
\right), $$
%
$$
v_{j}^{(k)}=\left\{
\begin{array}{ll}
c_{j-1}, & k=0\\
0,&k>0 \wedge \mbox{if}~j>N_S-k\\
v_{1}^{(k-1)}-v_{N_S-j}^{(k-1)} . \frac{v_{1}^{(k-1)}}{v_{N_S-k}^{(k-1)}}, &k>0 \wedge  \mbox{if}~j\leq N_S-k\\
\end{array}
\right.
$$
%
$S(z)$ is stable iif:
$$\phi_\mathit{stability} \equiv \textcolor{blue}{S(1) > 0}\ \uncover<2->{\wedge\ \textcolor{blue}{(-1)^{N_S} S(-1) > 0}}\ \uncover<3->{\wedge\ \textcolor{blue}{|c_0| < c_{N_S}}}\ \uncover<4>{\wedge\ \textcolor{blue}{\forall k, v_1^{(k)} > 0}}$$
\end{frame}

\begin{frame}{Transfer Functions and Uncertainty}
\begin{align*}
\small
\label{controller_plant_tf}
\hat{C}(z)&=\frac{\hat{C}_n(z)}{\hat{C}_d(z)}=\frac{\sum_{i=0}^{M_C}(\beta_{i}+\Delta\beta_{i}) z^{-i}}{\sum_{i=0}^{N_C}(\alpha_{i}+\Delta \alpha_{i}) z^{-i}}, \\
\\%\label{plant_tf}
\hat{G}(z)&=\frac{\hat{G}_n(z)}{\hat{G}_d(z)}=\frac{\sum_{i=0}^{M_G}(b_{i}+\Delta b_i) z^{-i}}{\sum_{i=0}^{N_G}(a_{i}+\Delta a_{i}) z^{-i}}.
\end{align*}
%
where $\vec{\beta}$ and $\vec{\alpha}$ are vectors containing the
controller's coefficients and $\vec{b}$ and $\vec{a}$ denote the
plant's coefficients.

@@

\begin{frame}{Sources of Uncertainty}
\setbeamertemplate{itemize items}[square]
\begin{itemize}
\item<1-> Model Parametric Errors (Affect $\Delta G(z)$)
\item<2-> Quantization Errors in the ADC, DAC, and controller arithmetic. 
(Modelled as external noise. Do not affect the transfer functions)
\item<3-> Roundoff Errors in the verification process (Affect $\Delta S(z)$)
\item<4-> Discretization Errors  (Affect $\Delta G(z)$ and $\Delta C(z)$)
\end{itemize}
\end{frame}

@@

%
\begin{frame}{Our Objective}
We seek to synthesise a controller where $\Delta \vec{\beta}=0$ and $\Delta \vec{\alpha}=0$ and which stabilizes all plants within a given range of $\Delta \vec{b}$ and $\Delta \vec{a}$.
\end{frame}

\begin{frame}[fragile]{Our CEGIS Model}
\begin{figure}[htb]
\centering
\resizebox{1.0\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=7cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \only<1,22>{\& \node[ellipse, fill=gray!20] (done) {{\sc Done}};}\\
   \& \\
   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search\\ \only<2-15>{$\textcolor{blue}{FP=\mathbb{R}\langle16,24\rangle}$}\only<16->{$\textcolor{blue}{FP=\mathbb{R}\langle20,28\rangle}$}};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based\\Verifier};
   \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Interval Arithmetic\\Verifier};
   }   
    \\
  };

>>>>

\begin{frame}{Stability Analysis via Jury's Criterion}

\begin{equation*}
S(z) = \hat{G}_n(z) \tilde{C}_n(z)+\hat{G}_d(z) \tilde{C}_d(z) = \sum_{i=0}^{N_S} c_iz^{N_s-i}, c_0 \neq 0 
\end{equation*}

$$
M=\left( 
\begin{array}{ccc}
v^{(0)}_{1} &\cdots & v^{(0)}_{N_S}\\
v^{(1)}_{1} &\cdots&  v^{(1)}_{N_S}\\
\vdots&\vdots&\vdots\\
v^{(N_S-1)}_{1} &\cdots&  v^{(N_S-1)}_{N_S}\\
\end{array}
\right), $$
%
$$
v_{j}^{(k)}=\left\{
\begin{array}{ll}
c_{j-1}, & k=0\\
0,&k>0 \wedge \mbox{if}~j>N_S-k\\
v_{1}^{(k-1)}-v_{N_S-j}^{(k-1)} . \frac{v_{1}^{(k-1)}}{v_{N_S-k}^{(k-1)}}, &k>0 \wedge  \mbox{if}~j\leq N_S-k\\
\end{array}
\right.
$$
%
$S(z)$ is stable $\Leftrightarrow$
$$
%\phi_\mathit{stability} \equiv 
\textcolor{blue}{S(1) > 0}\ \uncover<2->{\wedge\ \textcolor{blue}{(-1)^{N_S} S(-1) > 0}}\ \uncover<3->{\wedge\ \textcolor{blue}{|c_0| < c_{N_S}}}\ \uncover<4>{\wedge\ \textcolor{blue}{\forall k, v_1^{(k)} > 0}}
$$

@@

\begin{frame}{Transfer Functions and Uncertainty}

\begin{align*}
\small
\hat{C}(z)&=\frac{\hat{C}_n(z)}{\hat{C}_d(z)}=\frac{\sum_{i=0}^{M_C}(\beta_{i}+\Delta\beta_{i}) z^{-i}}{\sum_{i=0}^{N_C}(\alpha_{i}+\Delta \alpha_{i}) z^{-i}}, \\
\\%\label{plant_tf}
\hat{G}(z)&=\frac{\hat{G}_n(z)}{\hat{G}_d(z)}=\frac{\sum_{i=0}^{M_G}(b_{i}+\Delta b_i) z^{-i}}{\sum_{i=0}^{N_G}(a_{i}+\Delta a_{i}) z^{-i}}.
\end{align*}
%
\begin{itemize}
\item 
$\vec{\beta}$ and $\vec{\alpha}$ -- vectors containing controller coefficients 
\item 
$\vec{b}$ and $\vec{a}$ -- plant coefficients 
\end{itemize}

\begin{frame}{Sources of Uncertainty}
\setbeamertemplate{itemize items}[square]

\begin{itemize}
\item<1->[1.] Model Parametric Errors (affect $\Delta G(z)$)
\item<2->[2.] Quantisation errors in the ADC, DAC, and controller arithmetics  
(modelled as external noise, do not affect transfer functions)
\item<3->[3.] Roundoff errors in verification process (affect $\Delta S(z)$)
\item<4->[4.] Discretisation errors (affect $\Delta G(z)$ and $\Delta C(z)$) 
\end{itemize}
\end{frame}

@@

%
\begin{frame}{Our Objective}

We seek to synthesise a controller where $\Delta \vec{\beta}=0$ and $\Delta \vec{\alpha}=0$ and which stabilizes all plants within a given range of $\Delta \vec{b}$ and $\Delta \vec{a}$.

\begin{frame}[fragile]{CEGIS Architecture}
\begin{figure}[htb]
\centering
\resizebox{1.0\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=7cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
   } 
   \only<1,22>{\& \node[ellipse, fill=gray!20] (done) {{\sc Done}};}\\
   \& \\
   \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search\\ \only<2-15>{$\textcolor{blue}{FP=\mathbb{R}\langle16,24\rangle}$}\only<16->{$\textcolor{blue}{FP=\mathbb{R}\langle20,28\rangle}$}};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based\\Verifier};
   \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Interval Arithmetic\\Verifier};
   }   
    \\
  };
